Simplifying Parallel Graph Processing: \\ \large Survey of Existing Platforms

### 2016-11-28 report/survey.tex
Updated get graphalytics. Still doesn't work on mac.
Updated get-hwinfo and report specs towards the aim of getting
a csv output from graphalytics. Notices TEPS is not very well-
defined for graphalytics.

\section{Machine Specifications}
Below are the preliminary results by running two benchmarks on the research computer Arya.

% TODO: Make this a pgfplotstable with an automatically generated csv.
\begin{table}[htb]
	\centering
% Arya
%	\begin{tabular}{l|r}
%		CPU & 72 Core Intel Xeon E5 2699 v3\\ \hline
%		RAM & 256 GB DDR4 2133 MHz
%	\end{tabular}

@@

\begin{table}[htb]
	\centering
	\begin{tabular}{lr}
		Transport & \\ \hline
		Network Topology & \\ \hline
		Local Scheduling & \\ \hline
		Runtime Feedback & \\ \hline
		Approach & \\ \hline
		Algorithmic Considerations & \\ \hline
	\end{tabular}
	\caption{Middleware specifications}
	\label{tab:reportcard}
\end{table}

Performance in millions of traversed edges per second (MTEPS)

% TODO: This should be unnecessary once autogeneration is used.
\begin{table}[htb]
	\centering
	\begin{tabular}{l|r|r|}
	 & PowerGraph & OpenG \\ \hline
	BFS & $87.4$ & $341$ \\ \hline
	SSSP & $1.09$ & $3.08$ \\ \hline
	\end{tabular}
	\caption{Performance Results}
	\label{tab:perf}
\end{table}

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{table}
	\begin{minipage}{\linewidth} % So the footnotes all get printed on the same page
		\centering
		% \small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={Name,Type,HPC,Parallelism,Target,FOSS,Source,Notes},
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
%			columns/Comm./.style={%
%				string type,
%				postproc cell content/.style={%
%					@cell content/.add={\footnotesize}
%				}
%			},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{platforms.csv}
		\caption{Tools used for graph processing}
		\label{tab:frameworks}
	\end{minipage}
\end{table}

>>>>

\section{Machine Specifications}
Table~\ref{tab:specs} shows the specifications of the research computer (named Arya).

% TODO: Make this a pgfplotstable with an automatically generated csv.
\begin{table}[!htb]
	\centering
% Arya
%	\begin{tabular}{l|r}
%		CPU & 72 Core Intel Xeon E5 2699 v3\\ \hline
%		RAM & 256 GB DDR4 2133 MHz
%	\end{tabular}

@@

%\begin{table}[htb]
%	\centering
%	\begin{tabular}{lr}
%		Transport & \\ \hline
%		Network Topology & \\ \hline
%		Local Scheduling & \\ \hline
%		Runtime Feedback & \\ \hline
%		Approach & \\ \hline
%		Algorithmic Considerations & \\ \hline
%	\end{tabular}
%	\caption{Middleware specifications}
%	\label{tab:reportcard}
%\end{table}

\section{Performance}
Graphalytics without the use of the Granula plugin produces performance measurement in two forms: runtime in seconds and traversed edges per second.

Table~\ref{tab:perf} lists performance in millions of traversed edges per second (MTEPS) according to the graphalytics output. While this metric is simple to compute it is invariant across algorithms: for example, computing the local clustering coefficient involves traversing each edge multiple times (proportional to the sparsity of the graph), while breadth first search (BFS) traverses each edge exactly once, and on na\:ive implementations single-source shortest paths (SSSP) may have $O(|E| + |V|^2)$ traversed edges.
% TODO: Cite Comer algorithm book for Dijkstra's algorithm runtime.

% TODO: This should be unnecessary once autogeneration is used.
\begin{table}[!htb]
	\centering
	\begin{tabular}{l|r|r|}
	 & PowerGraph & OpenG \\ \hline
	BFS & 81.8 & 341 \\ \hline
	SSSP & 1.64 & 15.0 \\ \hline
	LCC & 54.6 & 142 \\ \hline
	\end{tabular}
	\caption{Performance Results for the \texttt{dota-league} dataset with 61,670 vertices and 50,870,313 edges. BFS is breadth-first search, SSSP is single-source shortest paths, LCC is local clustering coefficient.}
	\label{tab:perf}
\end{table}

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{table}[!htb]
	\begin{minipage}{\linewidth} % So the footnotes all get printed on the same page
		\centering
		% \small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={Name,Type,HPC,Parallelism,Target,FOSS,Source,Notes},
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
%			columns/Comm./.style={%
%				string type,
%				postproc cell content/.style={%
%					@cell content/.add={\footnotesize}
%				}
%			},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{platforms.csv}
		\caption{Tools used for graph processing}
		\label{tab:frameworks}
	\end{minipage}
\end{table}
